HealpixNet: Efficient spherical Convolutional Neural Network with HEALPix sampling for cosmological applications

### 2018-08-12 scnn.tex
small updates

Contrary to classical signal processing on Euclidean domains, the kernel $h$ has no single representation in the vertex domain and cannot be translated on the graph. It can however be \textit{localized} on any vertex $v_i$ by the convolution with a Kronecker delta\footnote{A Kronecker delta is the signal $\b \delta_i \in \R^{N_{pix}}$ that is zero everywhere except on vertex $v_i$ where it takes the value one.} $\b \delta_i \in \R^{N_{pix}}$. The localization operator $\T_i$ reads $\T_i h = h(\L) \b \delta_i = (h(\L))_i$, the $i$th column of $h(\L)$.
This localization of the kernel $h$ can be useful to visualize kernels, as explained in~\ref{sec:filter_visualization}.
If the graph is not regular, i.e., all nodes do not have the same number of neighbors, and all distances are not equal, the effect of the kernel will slightly differ from one node to another. While there is no perfect sampling of the sphere, these differences are negligible as the structure of the whole graph is very regular. However, when considering only parts of the sphere, one can observe important border effects (see \figref{border_effects} and~\ref{sec:border_effects}).

Finally, the graph convolution can be interpreted in the vertex domain as a scalar product with localizations $\T_i h$ of the kernel $h$. Indeed, the result of the convolution of the signal $\f$ with the kernel $h$ is
\begin{equation} \label{eqn:graph_convolution_spatial}
	(h(\L) \f)_i = \langle \T_i h(\L), \f \rangle = \langle h(\L) \b \delta_i, \f \rangle.
\end{equation}
To make the parallel with the classical 1D convolution, let $f, g\in \mathbb{Z} \rightarrow \mathbb{R}$ be two 1D discrete signals. Their convolution can be written in the same form as \eqnref{graph_convolution_spatial}:
\begin{equation*}
	(f \ast g) [i] = \sum_{j=-\infty}^\infty f[j] g[i-j] = \langle T_i g,  f \rangle,
\end{equation*}
where $T_i g[j] = g[i-j]$ is, up to a flip, a translation operator. 
% nati: I think now the indexing is clear and will not confuse with the rest of the paper.
Similarly as \eqnref{graph_convolution_spatial}, the convolution of the signal $f$ by a kernel $g$ is the scalar product of $f$ with translated versions $T_i g$ of the kernel $g$.
% Signals and kernels are the same thing in classical signal processing precisely because there exists a proper definition of translation.
% For Michael: I know what you mean here, but it is slightly more complicated than that. 
Additionally, it turns out that the localization operator $\T_i h$ is a generalization of the translation operator on graphs. In the particular case where the Laplacian matrix $\L$ is circulant, $\T_i h$ is a translated version of $\T_j h$ for all $i, j$ and both convolutions are equivalent. We refer the reader to \citet[Sec 2.2]{perraudin2017stationary} for a detailed discussion of the connection between translation $T_i$ and localization $\T_i$.

>>>>

Contrary to classical signal processing on Euclidean domains, the kernel $h$ has no single representation in the vertex domain and cannot be translated on the graph. It can however be \textit{localized} on any vertex $v_i$ by the convolution with a Kronecker delta\footnote{A Kronecker delta is the signal $\b \delta^i \in \R^{N_{pix}}$ that is zero everywhere except on vertex $v_i$ where it takes the value one.} $\b \delta^i \in \R^{N_{pix}}$. The localization operator $\T_i$ reads $\T_i h = h(\L) \b \delta^i = (h(\L))_i$, the $i$th column of $h(\L)$.
This localization of the kernel $h$ can be useful to visualize kernels, as explained in~\ref{sec:filter_visualization}.
If the graph is not regular, i.e., all nodes do not have the same number of neighbors, and all distances are not equal, the effect of the kernel will slightly differ from one node to another. While there is no perfect sampling of the sphere, these differences are negligible as the structure of the whole graph is very regular. However, when considering only parts of the sphere, one can observe important border effects (see \figref{border_effects} and~\ref{sec:border_effects}).

Finally, the graph convolution can be interpreted in the vertex domain as a scalar product with localizations $\T_i h$ of the kernel $h$. Indeed, the result of the convolution of the signal $\f$ with the kernel $h$ is
\begin{equation} \label{eqn:graph_convolution_spatial}
	(h(\L) \f)_i = \langle \T_i h(\L), \f \rangle = \langle h(\L) \b \delta^i, \f \rangle.
\end{equation}
To make the parallel with the classical 1D convolution, let $f, g\in \mathbb{Z} \rightarrow \mathbb{R}$ be two 1D discrete signals. Their convolution can be written in the same form as \eqnref{graph_convolution_spatial}:
\begin{equation*}
	(f \ast g) [i] = \sum_{j=-\infty}^\infty f[j] g[i-j] = \langle T_i g,  f \rangle,
\end{equation*}
where $T_i g[j] = g[i-j]$ is, up to a flip, a translation operator. 
% nati: I think now the indexing is clear and will not confuse with the rest of the paper.
Similarly as \eqnref{graph_convolution_spatial}, the convolution of the signal $f$ by a kernel $g$ is the scalar product of $f$ with translated versions $T_i g$ of the kernel $g$.
% Signals and kernels are the same thing in classical signal processing precisely because there exists a proper definition of translation.
% For Michael: I know what you mean here, but it is slightly more complicated than that. 
Additionally, it turns out that the localization operator $\T_i h$ is a generalization of the translation operator on graphs. In the particular case where the Laplacian matrix $\L$ is circulant, $\T_i h$ is a translated version of $\T_j h$ for all $i, j$ and both convolutions are equivalent. We refer the reader to \citet[Sec 2.2]{perraudin2017stationary} for a detailed discussion of the connection between translation $T_i$ and localization $\T_i$.
